My Cool Title

### 2019-05-05 paper.tex
Added new schematic to experiment section

For this experiment, a mobile camera and object detector acts as the participant's eyes and informs them what the objects within the camera's view and it is then up to the participant to exploit their prior knowledge of the given environment in order to manipulate the camera to point towards the target object. 
This process is modelled by the schematic in Fig. MEME\todo{put in figure without controller} where the human, \emph{H}, acts as both the actuator and controller.
The object detector was implemented in an Android app that uses the object classifier and Android's Text-to-Speech engine to read out any objects that it detected. 
The app only reads out the objects when the participant requested it to by tapping on the screen. 
When the target object comes within the camera's view and is correctly classified by the object detector, the device vibrated to inform the participant.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
  \caption{A set of boxplots comparing the time to target. }\label{fig:boxplot-time}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/cumplot_time_to_target.png}
  \caption{A set of CDFs comparing the time to target. }\label{fig:cum-time}
\end{figure}

>>>>

For this experiment, a mobile camera and object detector acts as the participant's eyes and informs them what the objects within the camera's view and it is then up to the participant to exploit their prior knowledge of the given environment in order to manipulate the camera to point towards the target object. 
This process is modelled by the schematic in Fig.~\ref{fig:sys-diagram-no-controller}, \emph{H}, acts as both the actuator and controller.
The object detector was implemented in an Android app that uses the object classifier and Android's Text-to-Speech engine to read out any objects that it detected. 
The app only reads out the objects when the participant requested it to by tapping on the screen. 
When the target object comes within the camera's view and is correctly classified by the object detector, the device vibrated to inform the participant.

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/control_loop_no_controller.png}
  \caption{A set of CDFs comparing the time to target. }\label{fig:sys-diagram-no-controller}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
  \caption{A set of boxplots comparing the time to target. }\label{fig:boxplot-time}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/cumplot_time_to_target.png}
  \caption{A set of CDFs comparing the time to target. }\label{fig:cum-time}
\end{figure}
